On Extending a Full-Sharing Design with Batched Scheduling

### 2015-04-15 paper.tex
batched scheduling ->ok for now

Multithreading in Prolog is the ability to concurrently perform
computations, in which each computation runs independently but shares
the program clauses. When multithreading is combined with tabling, we
have the best of both worlds, since we can exploit the combination of
higher procedural control with higher declarative semantics. To the
best of our knowledge, XSB~\cite{Marques-08} and Yap~\cite{Areias-12a}
were the only Prolog systems that were able to combine both
multithreading with tabling. Yap's threads have their own execution
stacks and only share the code area where predicates, records, flags
and other global non-backtrackable data are stored. For tabled
evaluation, a thread views its tables as private but, at the engine
level, Yap has three designs that vary from a \emph{No-Sharing} (NS)
design, where each thread allocates fully private tables for each new
tabled subgoal called during its computation, to a \emph{Full-Sharing}
(FS), where threads share the complete table space.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Yap's No-Sharing and Full-Sharing Designs}

\begin{figure}[!ht]
\centering
\includegraphics[width=10.5cm]{figures/arch.pdf}
\caption{The \emph{FS} design with the PAC procedure - (a) private
  chaining and (b) public chaining}
\label{fig_tabtries_pcc}
\end{figure}

@@

@@

Figure~\ref{fig_tabtries_pcc} shows the key data structures for
supporting the implementation of the PAC procedure during the
evaluation of a tabled subgoal call $P_{i.j}$ using the FS design. The
FS design, uses a subgoal entry data structure to store common
information for a subgoal call and a subgoal frame (\emph{SF}) data
structure to store private information about the execution of each
thread. The PAC procedure works at the subgoal frame level, which is
private to each thread.

@@

Figure~\ref{fig_tabtries_pcc}(a) shows then a situation where two
threads, $T_1$ and $T_{k-1}$, are sharing the same subgoal entry call
$P_{i.j}$ when the subgoal is still under evaluation, i.e., the
subgoal is not yet complete. The current state of the evaluation shows
an answer trie with $3$ answers found for the subgoal call
$P_{i.j}$. For the sake of simplicity, we are omitting the internal
answer trie nodes and we are only showing the leaf nodes nodes $LN_1$,
$LN_2$ and $LN_3$, in the figure. With the PAC procedure, the leaf
nodes are not chained in the \emph{AT} data structure. Now, the
chaining process is done privately, and for that, we use the subgoal
frame structure of each thread. On the subgoal frame structure we
added a new field, called \emph{consumer}, to store the answers found
within the execution of the thread. In order to minimize the impact of
the \emph{PAC} optimization, each node within the new consumer answer
structure has two fields: (i) an entry pointer, which points to the
corresponding leaf node in the answer trie data structure; (ii) a next
pointer to chain the answers within the consumer structure. To
maintain a good performance, when the number of nodes exceeds a
certain threshold, we use a hash trie mechanism design similar to the
one presented in the work~\cite{Areias-ijpp15}. However, since this
mechanism is private to each thread, it does not require any of the
tools that were necessary to support concurrency. In particular, on
each hash trie level, we have removed the tools necessary to support
concurrency, such as useless pointers and compare-and-swap
operations. We have chosen this hashing mechanism, because it showed a
good balance between lookup and insert
operations~\cite{Areias-ijpp15}, but the major reason was mostly
because of the integration in the TabMalloc memory
allocator~\cite{Areias-12b}.

@@

We used five sets of benchmarks. The \emph{Large Joins} and
\emph{WordNet} sets were obtained from the OpenRuleBench
project~\cite{Liang-09}; the \emph{Model Checking} set includes three
different specifications and transition relation graphs usually used
in model checking applications; the \emph{Path Left} and \emph{Path
  Right} sets implement two recursive definitions of the well-known
$path/2$ predicate, that computes the transitive closure in a graph,
using several different configurations of $edge/2$ facts. We
experimented graphs with the \emph{BTree} configuration with depth 17,
the \emph{Pyramid} and \emph{Cycle} configurations with depth 2000 and
the \emph{Grid} configuration with depth 35.

In order to have a deeper insight on the behavior of each benchmark,
and therefore clarify some of the results that are presented next, we
first characterize the benchmarks. The columns in
Table~\ref{tab_benchs} have the following meaning: (i) {\bf calls:} is
the number of different calls to tabled subgoals. It corresponds to
the number of paths in the subgoal tries. (ii) {\bf trie nodes:} is
the total number of trie nodes allocated in the corresponding
subgoal/answer trie structures. (iii) {\bf trie depth:} is the
minimum/average/maximum number of trie node levels required to
represent a path in the corresponding subgoal/answer trie
structures. Trie structures with smaller average values are more
amenable to higher lock contention. (iv) {\bf unique:} is the number
of different tabled answers found. It corresponds to the number of
paths in the answer tries. (v) {\bf repeated:} is the number of
redundant tabled answers found. (vi) {\bf NS:} is the average
execution time, in seconds, of ten runs for 1 thread with the NS
design without the TabMalloc memory allocator. In what follows, we
will use these times as the base times when computing the overhead
ratios for the other designs.

By observing Table~\ref{tab_benchs}, the \emph{Mondial} benchmark,
from the \emph{Large Joins} set, and the three \emph{Model
  Checking} benchmarks seem to be the benchmarks least amenable to
lock contention since they are the ones that find less unique answers
and that have the deepest trie structures. In this regard, the
\emph{Path Left} and \emph{Path Right} sets correspond to the
opposite case. They find a huge number of answers and have very
shallow trie structures. On the other hand, the \emph{WordNet} and
\emph{Path Right} sets have the benchmarks with the largest number
of different subgoal calls, which can reduce the probability of lock
contention because answers can be found for different subgoal calls
and therefore be inserted with minimum overlap. On the opposite side
are the \emph{Join2} benchmark, from the \emph{Large Joins} set,
and the \emph{Path Left} benchmarks, which have only a single tabled
subgoal call.

\begin{table}[ht]
\centering
\caption{Characteristics of the benchmark programs}
\scalebox{0.82} { 
\begin{tabular}{lrrccrrrcc}
\hline\hline
\multirow{2}{*}{\bf Bench}
& \multicolumn{3}{c}{\bf Tabled Subgoals}
&
& \multicolumn{4}{c}{\bf Tabled Answers}
& \multicolumn{1}{c}{\bf Time (sec)} \\ \cline{2-4}\cline{6-9}
& \multicolumn{1}{c}{\bf calls}
& \multicolumn{1}{c}{\bf trie nodes}
& \multicolumn{1}{c}{\bf trie depth}
&
& \multicolumn{1}{c}{\bf unique}
& \multicolumn{1}{c}{\bf repeated}
& \multicolumn{1}{c}{\bf trie nodes}
& \multicolumn{1}{c}{\bf trie depth}
& \multicolumn{1}{c}{\bf NS} \\
\hline
\multicolumn{10}{l}{\bf Large Joins} \\
\bf{Join2}    &       1 &       6 & 5/5/5 && 2,476,099 &         0 &
2,613,660 &    5/5/5 &  2.85 \\
\bf{Mondial}  &      35 &      42 & 3/4/4 &&     2,664 & 2,452,890 &
   14,334 &    6/7/7 &  0.84 \\
\hline
\multicolumn{10}{l}{\bf WordNet} \\
\bf{Clusters} & 117,659 & 235,319 & 2/2/2 &&   166,877 &   161,853 &
284,536 &    1/1/1 &   0.83 \\
\bf{Holo}     & 117,657 & 235,315 & 2/2/2 &&    74,838 &        54 &
192,495 &    1/1/1 &   0.75 \\
\bf{Hyper}    & 117,657 & 235,315 & 2/2/2 &&   698,472 &     8,658 &
816,129 &    1/1/1 &   1.42 \\
\bf{Hypo}     & 117,657 & 117,659 & 2/2/2 &&   698,472 &    20,341 &
816,129 &    1/1/1 &   1.53 \\
\bf{Mero}     & 117,657 & 117,659 & 2/2/2 &&    74,838 &        13 &
192,495 &    1/1/1 &   0.74 \\
\bf{Tropo}    & 117,657 & 235,315 & 2/2/2 &&       472 &         0 &
118,129 &    1/1/1 &   0.66 \\
\hline
\multicolumn{10}{l}{\bf Model Checking} \\
\bf{IProto}   &       1 &       6 & 5/5/5 &&   134,361 &   385,423 &
1,554,896 &  4/51/67 & 2.70 \\
\bf{Leader}   &       1 &       5 & 4/4/4 &&     1,728 &   574,786 &
   41,788 & 15/80/97 & 3.51  \\
\bf{Sieve}    &       1 &       7 & 6/6/6 &&       380 & 1,386,181 &
    8,624 & 21/53/58 & 18.50 \\
\hline
\multicolumn{10}{l}{\bf Path Left} \\
\bf{BTree}    &       1 &       3 & 2/2/2 && 1,966,082 &         0 &
2,031,618 &    2/2/2 &   1.53 \\
\bf{Cycle}    &       1 &       3 & 2/2/2 && 4,000,000 &     2,000 &
4,002,001 &    2/2/2 &   3.52 \\
\bf{Grid}     &       1 &       3 & 2/2/2 && 1,500,625 & 4,335,135 &
1,501,851 &    2/2/2 &  1.93 \\
\bf{Pyramid}  &       1 &       3 & 2/2/2 && 3,374,250 & 1,124,250 &
3,377,250 &    2/2/2 &   3.08 \\
\hline
\multicolumn{10}{l}{\bf Path Right} \\
\bf{BTree}    & 131,071 & 262,143 & 2/2/2 && 3,801,094 &         0 &
3,997,700 &    1/2/2 &  2.33 \\
\bf{Cycle}    &   2,001 &   4,003 & 2/2/2 && 8,000,000 &     4,000 &
8,004,001 &    1/2/2 &  3.55 \\
\bf{Grid}     &   1,226 &   2,453 & 2/2/2 && 3,001,250 & 8,670,270 &
3,003,701 &    1/2/2 &  2.32 \\
\bf{Pyramid}  &   3,000 &   6,001 & 2/2/2 && 6,745,501 & 2,247,001 &
6,751,500 &    1/2/2 &  3.17 \\
\hline\hline
\end{tabular}}
\label{tab_benchs}
\end{table}

Note that for the moment our goal is to evaluate the robustness of our
implementation when exposed to \emph{worst case} scenarios. By
focusing on \emph{worst case} scenarios, we show the lowest bounds in
terms of performance that each design might achieve when applied/used
with other real world applications/programs. Moreover, by testing the
framework with worst case scenarios, we avoid the peculiarities of the
program at hand and we try to focus on measuring the real value of our
designs. Thus, we will follow a common approach to create worst case
scenarios and we will run all threads starting with the same query
goal. By doing this, it is expected that all threads will access the
table space, to check/insert for subgoals and answers, at similar
times, thus causing a huge stress on the same critical regions. To put
the results in perspective, we experimented with $1$, $8$, $16$, $24$
and $32$ threads (the maximum number of cores available in our
machine) with local and batched scheduling on the five sets of
benchmarks presented in the early subsection.

>>>>

Multithreading in Prolog is the ability to concurrently perform
computations, in which each computation runs independently but shares
the program clauses. When multithreading is combined with tabling, we
have the best of both worlds, since we can exploit the combination of
higher procedural control with higher declarative semantics. To the
best of our knowledge, XSB~\cite{Marques-08} and Yap~\cite{Areias-12a}
were the only Prolog systems that were able to combine both
multithreading with tabling. Yap implements a SWI-Prolog compatible
multi-threading library~\cite{Wielemaker-03}. Yap's threads have their
own execution stacks and only share the code area where predicates,
records, flags and other global non-backtrackable data are stored. For
tabled evaluation, a thread views its tables as private but, at the
engine level, Yap has three designs that vary from a \emph{No-Sharing}
(NS) design, where each thread allocates fully private tables for each
new tabled subgoal called during its computation, to a
\emph{Full-Sharing} (FS), where threads share the complete table
space.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Table Space Organization}

The basic idea behind tabling is straightforward: programs are
evaluated by storing answers for tabled subgoals in an appropriate
data space, called the \emph{table space}. Similar calls to tabled
subgoals are not re-evaluated against the program clauses, instead
they are resolved by consuming the answers already stored in their
table entries. During this process, as further new answers are found,
they are stored in their tables and later returned to all similar
calls.

\begin{wrapfigure}{r}{4.5cm}
\vspace{-\intextsep}
\centering
\includegraphics[width=4.5cm]{figures/table-space.pdf}
\caption{Table space organization}
\label{fig_table_space}
\vspace{-0.5\intextsep}
\end{wrapfigure}

Figure~\ref{fig_table_space} shows the table space organization of the
Yap system. At the entry point we have the \emph{table entry} data
structure. This structure is allocated when a tabled predicate is
being compiled, so that a pointer to the table entry can be included
in its compiled code. This guarantees that further calls to the
predicate will access the table space starting from the same
point. Below the table entry, we have the \emph{subgoal trie
  structure}. Each different tabled subgoal call to the predicate at
hand corresponds to a unique path through the subgoal trie structure,
always starting from the table entry, passing by several subgoal trie
data units, the \emph{subgoal trie nodes}, and reaching a leaf data
structure, the \emph{subgoal frame}. The subgoal frame stores
additional information about the subgoal and acts like an entry point
to the \emph{answer trie structure}. Each unique path through the
answer trie data units, the \emph{answer trie nodes}, corresponds to a
different answer to the entry subgoal.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Yap's Multithreaded Tabling Support}

Yap implements a SWI-Prolog compatible multi-threading
library~\cite{Wielemaker-03}. Like in SWI-Prolog, Yap's threads have
their own execution stacks and only share the code area where
predicates, records, flags and other global non-backtrackable data are
stored.

In a multithreaded tabling evaluation, a thread views its tables as
private but, at the engine level, Yap has three designs that vary from
a \emph{No-Sharing} (NS) design, where each thread allocates fully
private tables for each new tabled subgoal called during its
computation, to a \emph{Full-Sharing} (FS), where threads share the
complete table space. Figure~\ref{fig_table_space} shows Yap's
multithreaded tabling support with an abstraction layer to which
threads interact (the threads represented in the bottom of the
figure), and at the engine level the configuration of the NS and FS
designs in a situation where several different threads evaluated the
same tabled subgoal call $i$.

In the NS design, each thread allocates fully private tables for each
new subgoal called during its computation. One can observe that the
table entry data structure still stores the common information for the
predicate (such as the arity or the evaluation strategy), and then
each thread $t$ has its own cell $T_t$ inside a \emph{bucket array}
which points to the private data structures.

\begin{figure}[!ht]
\centering
\includegraphics[width=10.5cm]{figures/yap-mt.pdf}
\caption{Yap's multithreaded tabled space using the NS and FS designs}
\label{fig_yap_mt_support}
\end{figure}

In the FS design, part of the subgoal frame information (the
\emph{subgoal entry} data structure) and the answer trie structure are
now shared among all threads. The previous subgoal frame data
structure was split into two: the \emph{subgoal entry} stores common
information for the subgoal call (such as the pointer to the shared
answer trie structure); the remaining information (the \emph{subgoal
  frame} data structure) remains private to each thread.

@@

@@

In this section, we show how we have extended the FS design to support
batched scheduling.

@@

Figure~\ref{fig_tabtries_pcc} shows the key data structures for
supporting the implementation of the PAC procedure during the
evaluation of a tabled subgoal call $i$ using the FS design. The FS
design, uses a subgoal entry data structure to store common
information for a subgoal call and a subgoal frame (\emph{SF}) data
structure to store private information about the execution of each
thread. The PAC procedure works at the subgoal frame level, which is
private to each thread.

@@

Figure~\ref{fig_tabtries_pcc}(a) shows then a situation where two
threads, $T_1$ and $T_{k-1}$, are sharing the same subgoal entry call
$i$ when the subgoal is still under evaluation, i.e., the subgoal is
not yet complete. The current state of the evaluation shows an answer
trie with $3$ answers found for the subgoal call $i$. For the sake of
simplicity, we are omitting the internal answer trie nodes and we are
only showing the leaf nodes nodes $LN_1$, $LN_2$ and $LN_3$, in the
figure. With the PAC procedure, the leaf nodes are not chained in the
\emph{AT} data structure. Now, the chaining process is done privately,
and for that, we use the subgoal frame structure of each thread. On
the subgoal frame structure we added a new field, called
\emph{consumer}, to store the answers found within the execution of
the thread. In order to minimize the impact of the \emph{PAC}
optimization, each node within the new consumer answer structure has
two fields: (i) an entry pointer, which points to the corresponding
leaf node in the answer trie data structure; (ii) a next pointer to
chain the answers within the consumer structure. To maintain a good
performance, when the number of nodes exceeds a certain threshold, we
use a hash trie mechanism design similar to the one presented in the
work~\cite{Areias-ijpp15}. However, since this mechanism is private to
each thread, it does not require any of the tools that were necessary
to support concurrency. In particular, on each hash trie level, we
have removed the tools necessary to support concurrency, such as
useless pointers and compare-and-swap operations. We have chosen this
hashing mechanism, because it showed a good balance between lookup and
insert operations~\cite{Areias-ijpp15}, but the major reason was
mostly because of the integration in the TabMalloc memory
allocator~\cite{Areias-12b}.

@@

%% We used five sets of benchmarks. The \emph{Large Joins} and
%% \emph{WordNet} sets were obtained from the OpenRuleBench
%% project~\cite{Liang-09}; the \emph{Model Checking} set includes three
%% different specifications and transition relation graphs usually used
%% in model checking applications; the \emph{Path Left} and \emph{Path
%%   Right} sets implement two recursive definitions of the well-known
%% $path/2$ predicate, that computes the transitive closure in a graph,
%% using several different configurations of $edge/2$ facts. We
%% experimented graphs with the \emph{BTree} configuration with depth 17,
%% the \emph{Pyramid} and \emph{Cycle} configurations with depth 2000 and
%% the \emph{Grid} configuration with depth 35.

%% In order to have a deeper insight on the behavior of each benchmark,
%% and therefore clarify some of the results that are presented next, we
%% first characterize the benchmarks. The columns in
%% Table~\ref{tab_benchs} have the following meaning: (i) {\bf calls:} is
%% the number of different calls to tabled subgoals. It corresponds to
%% the number of paths in the subgoal tries. (ii) {\bf trie nodes:} is
%% the total number of trie nodes allocated in the corresponding
%% subgoal/answer trie structures. (iii) {\bf trie depth:} is the
%% minimum/average/maximum number of trie node levels required to
%% represent a path in the corresponding subgoal/answer trie
%% structures. Trie structures with smaller average values are more
%% amenable to higher lock contention. (iv) {\bf unique:} is the number
%% of different tabled answers found. It corresponds to the number of
%% paths in the answer tries. (v) {\bf repeated:} is the number of
%% redundant tabled answers found. (vi) {\bf NS:} is the average
%% execution time, in seconds, of ten runs for 1 thread with the NS
%% design without the TabMalloc memory allocator. In what follows, we
%% will use these times as the base times when computing the overhead
%% ratios for the other designs.

%% By observing Table~\ref{tab_benchs}, the \emph{Mondial} benchmark,
%% from the \emph{Large Joins} set, and the three \emph{Model
%%   Checking} benchmarks seem to be the benchmarks least amenable to
%% lock contention since they are the ones that find less unique answers
%% and that have the deepest trie structures. In this regard, the
%% \emph{Path Left} and \emph{Path Right} sets correspond to the
%% opposite case. They find a huge number of answers and have very
%% shallow trie structures. On the other hand, the \emph{WordNet} and
%% \emph{Path Right} sets have the benchmarks with the largest number
%% of different subgoal calls, which can reduce the probability of lock
%% contention because answers can be found for different subgoal calls
%% and therefore be inserted with minimum overlap. On the opposite side
%% are the \emph{Join2} benchmark, from the \emph{Large Joins} set,
%% and the \emph{Path Left} benchmarks, which have only a single tabled
%% subgoal call.

%% \begin{table}[ht]
%% \centering
%% \caption{Characteristics of the benchmark programs}
%% \scalebox{0.82} { 
%% \begin{tabular}{lrrccrrrcc}
%% \hline\hline
%% \multirow{2}{*}{\bf Bench}
%% & \multicolumn{3}{c}{\bf Tabled Subgoals}
%% &
%% & \multicolumn{4}{c}{\bf Tabled Answers}
%% & \multicolumn{1}{c}{\bf Time (sec)} \\ \cline{2-4}\cline{6-9}
%% & \multicolumn{1}{c}{\bf calls}
%% & \multicolumn{1}{c}{\bf trie nodes}
%% & \multicolumn{1}{c}{\bf trie depth}
%% &
%% & \multicolumn{1}{c}{\bf unique}
%% & \multicolumn{1}{c}{\bf repeated}
%% & \multicolumn{1}{c}{\bf trie nodes}
%% & \multicolumn{1}{c}{\bf trie depth}
%% & \multicolumn{1}{c}{\bf NS} \\
%% \hline
%% \multicolumn{10}{l}{\bf Large Joins} \\
%% \bf{Join2}    &       1 &       6 & 5/5/5 && 2,476,099 &         0 &
%% 2,613,660 &    5/5/5 &  2.85 \\
%% \bf{Mondial}  &      35 &      42 & 3/4/4 &&     2,664 & 2,452,890 &
%%    14,334 &    6/7/7 &  0.84 \\
%% \hline
%% \multicolumn{10}{l}{\bf WordNet} \\
%% \bf{Clusters} & 117,659 & 235,319 & 2/2/2 &&   166,877 &   161,853 &
%% 284,536 &    1/1/1 &   0.83 \\
%% \bf{Holo}     & 117,657 & 235,315 & 2/2/2 &&    74,838 &        54 &
%% 192,495 &    1/1/1 &   0.75 \\
%% \bf{Hyper}    & 117,657 & 235,315 & 2/2/2 &&   698,472 &     8,658 &
%% 816,129 &    1/1/1 &   1.42 \\
%% \bf{Hypo}     & 117,657 & 117,659 & 2/2/2 &&   698,472 &    20,341 &
%% 816,129 &    1/1/1 &   1.53 \\
%% \bf{Mero}     & 117,657 & 117,659 & 2/2/2 &&    74,838 &        13 &
%% 192,495 &    1/1/1 &   0.74 \\
%% \bf{Tropo}    & 117,657 & 235,315 & 2/2/2 &&       472 &         0 &
%% 118,129 &    1/1/1 &   0.66 \\
%% \hline
%% \multicolumn{10}{l}{\bf Model Checking} \\
%% \bf{IProto}   &       1 &       6 & 5/5/5 &&   134,361 &   385,423 &
%% 1,554,896 &  4/51/67 & 2.70 \\
%% \bf{Leader}   &       1 &       5 & 4/4/4 &&     1,728 &   574,786 &
%%    41,788 & 15/80/97 & 3.51  \\
%% \bf{Sieve}    &       1 &       7 & 6/6/6 &&       380 & 1,386,181 &
%%     8,624 & 21/53/58 & 18.50 \\
%% \hline
%% \multicolumn{10}{l}{\bf Path Left} \\
%% \bf{BTree}    &       1 &       3 & 2/2/2 && 1,966,082 &         0 &
%% 2,031,618 &    2/2/2 &   1.53 \\
%% \bf{Cycle}    &       1 &       3 & 2/2/2 && 4,000,000 &     2,000 &
%% 4,002,001 &    2/2/2 &   3.52 \\
%% \bf{Grid}     &       1 &       3 & 2/2/2 && 1,500,625 & 4,335,135 &
%% 1,501,851 &    2/2/2 &  1.93 \\
%% \bf{Pyramid}  &       1 &       3 & 2/2/2 && 3,374,250 & 1,124,250 &
%% 3,377,250 &    2/2/2 &   3.08 \\
%% \hline
%% \multicolumn{10}{l}{\bf Path Right} \\
%% \bf{BTree}    & 131,071 & 262,143 & 2/2/2 && 3,801,094 &         0 &
%% 3,997,700 &    1/2/2 &  2.33 \\
%% \bf{Cycle}    &   2,001 &   4,003 & 2/2/2 && 8,000,000 &     4,000 &
%% 8,004,001 &    1/2/2 &  3.55 \\
%% \bf{Grid}     &   1,226 &   2,453 & 2/2/2 && 3,001,250 & 8,670,270 &
%% 3,003,701 &    1/2/2 &  2.32 \\
%% \bf{Pyramid}  &   3,000 &   6,001 & 2/2/2 && 6,745,501 & 2,247,001 &
%% 6,751,500 &    1/2/2 &  3.17 \\
%% \hline\hline
%% \end{tabular}}
%% \label{tab_benchs}
%% \end{table}

%% Note that for the moment our goal is to evaluate the robustness of our
%% implementation when exposed to \emph{worst case} scenarios. By
%% focusing on \emph{worst case} scenarios, we show the lowest bounds in
%% terms of performance that each design might achieve when applied/used
%% with other real world applications/programs. Moreover, by testing the
%% framework with worst case scenarios, we avoid the peculiarities of the
%% program at hand and we try to focus on measuring the real value of our
%% designs. Thus, we will follow a common approach to create worst case
%% scenarios and we will run all threads starting with the same query
%% goal. By doing this, it is expected that all threads will access the
%% table space, to check/insert for subgoals and answers, at similar
%% times, thus causing a huge stress on the same critical regions. To put
%% the results in perspective, we experimented with $1$, $8$, $16$, $24$
%% and $32$ threads (the maximum number of cores available in our
%% machine) with local and batched scheduling on the five sets of
%% benchmarks presented in the early subsection.
